---
title: "hmk_08"
format: gfm
editor: visual
---

## JOINS

First, I loaded the appropriate packages and create flights2 object.

```{r, message = FALSE}
library(tidyverse)
library(nycflights13)

flights2 <- flights |>
  select(year, time_hour, origin, dest, tailnum, carrier)
```

1.  "Imagine you've found the top 10 most popular destinations using this code:"

I created my top 10 destinations object and then used view to see the top 10 most popular destinations:

```{r}
top_dest <- flights2 |> 
  count(dest, sort = TRUE) |> 
  head(10)

view(top_dest)
```

Now, to see all flights to those destinations, I created the all_flights object, then I used left_join to join top_dest with flights2, but only by "dest", because that's the only column we are concerned with in this situation:

```{r}
all_flights <- top_dest |> 
  left_join(flights2, by = "dest") 
```

I checked to make sure that both have 10 destinations by using "\|\> count (dest)" for each in the console.

## FUNCTIONS

2.  "Write a function to 'rescale' a numeric vector by subtracting the mean of the vector from each element and then dividing each element by the standard deviation:"

The 'funct' vector I created below contains values 1-10. Then I used 'rescale' to create a function of my x (column of data).

```{r}
funct <- c(1:10)
```

This is where I created my function(x) to subtract the mean (x) from the original (x) value, then divded by the standard dev (sd) as instructed.

```{r}
rescale <- function(x) { 
  x - mean(x) / sd(x) 
  } 
```

Then I used 'funct2' as my new object that contains the rescaled 'funct' using the function of x equation I created above. This gives me the output of my function (x - mean(x) / sd(x)) for each of my vector integers. Then I used the view function to see the values in a table.

```{r}
funct2 <- rescale(funct)
view(funct2)
```
